Consensus Problems in Networks of Agents\\ with Switching Topology and Time-Delays

### 2020-10-28 Paper.tex
Adjust Content Page
Complete Chapter Appendix

% 正文开始
\begin{document}
\maketitle
% 生成目录
\tableofcontents

\begin{abstract}
{\color[gray]{0.5}
In this paper, we discuss consensus problems for a network of dynamic agents with ﬁxed and switching topologies. 
We analyze three cases: i) networks with switching topology and no time-delays, ii) networks with ﬁxed topology and communication time-delays, and iii) max-consensus problems (or leader determination) for groups of discrete-time agents. 
In each case, we introduce a linear/nonlinear consensus protocol and provide convergence analysis for the proposed distributed algorithm. 
Moreover, we establish a connection between the Fiedler eigenvalue of the information ﬂow in a network (i.e. algebraic connectivity of the network) and the negotiation speed (or performance) of the corresponding agreement protocol. 
It turns out that balanced digraphs play an important role in addressing average-consensus problems. 
We introduce disagreement functions that play the role of Lyapunov functions in convergence analysis of consensus protocols. 
A distinctive feature of this work is to address consensus problems for networks with directed information ﬂow. 
We provide analytical tools that rely on algebraic graph theory, matrix theory, and control theory. 
Simulations are provided that demonstrate the eﬀectiveness of our theoretical results.
}

@@

% ------------------------------------------------------------------------------
\section{Introduction}
{\color[gray]{0.5}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].
}

@@

{\color[gray]{0.5}
\noindent Moreover, for $\tau=\tau^*$ the system has a globally asymptotically stabel oscillatory solution with frequency $w=\lambda_n$. 
}

@@

>>>>

% 正文开始
\begin{document}
\maketitle

% \clearpage
\begin{abstract}
{\color[gray]{0.5}
In this paper, we discuss consensus problems for a network of dynamic agents with ﬁxed and switching topologies. 
We analyze three cases: i) networks with switching topology and no time-delays, ii) networks with ﬁxed topology and communication time-delays, and iii) max-consensus problems (or leader determination) for groups of discrete-time agents. 
In each case, we introduce a linear/nonlinear consensus protocol and provide convergence analysis for the proposed distributed algorithm. 
Moreover, we establish a connection between the Fiedler eigenvalue of the information ﬂow in a network (i.e. algebraic connectivity of the network) and the negotiation speed (or performance) of the corresponding agreement protocol. 
It turns out that balanced digraphs play an important role in addressing average-consensus problems. 
We introduce disagreement functions that play the role of Lyapunov functions in convergence analysis of consensus protocols. 
A distinctive feature of this work is to address consensus problems for networks with directed information ﬂow. 
We provide analytical tools that rely on algebraic graph theory, matrix theory, and control theory. 
Simulations are provided that demonstrate the eﬀectiveness of our theoretical results.
}

@@

\clearpage
% 生成目录
\tableofcontents

\clearpage
% ------------------------------------------------------------------------------
\section{Introduction}
{\color[gray]{0.5}
Distributed decision-making for coordination of networks of dynamic agents has attracted several researchers in recent years. 
This is partly due to broad applications of multi-agent systems in many areas including cooperative control of unmanned air vehicles (UAVs), ﬂocking of birds [22, 24, 23], schooling for underwater vehicles, distributed sensory networks, attitude alignment of clusters of satellites, and congestion control in communication networks [21].
}

@@

{\color[gray]{0.5}
\noindent Moreover, for $\tau=\tau^*$ the system has a globally asymptotically stable oscillatory solution with frequency $w=\lambda_n$. 
}

@@

% ------------------------------------------------------------------------------
\section*{A Appendix}
{\color[gray]{0.5}
This section contains the proofs of some of the theorems of the paper.
}

这部分包含了文章中一些定理的证明。

\subsection*{A.1 Proof of Theorem 1}
{\color[gray]{0.5}
\noindent \textbf{Proof.} Deﬁne $\phi_{ij}(z) = a_{ij}z$ for all $ij \in \mathcal{E}$. 
It is trivial that if $x_i=x_j$ for all $ij \in \mathcal{E}$, then $u=0$. 
Thus, we prove the converse: $u=0$ implies that all nodes are in agreement. 
If the values of all nodes are equal, the result follows. 
Thus, assume there exists a node $i^*$, called max-leader, such that $x_{i^*}\ge x_j$ for all $j\ne i^*$, i.e. $i^* = arg\max_{j\in \mathcal{I}} x_j$ (if $i^*$ is not unique, choose one arbitrarily).
}

\noindent 定义所有的$ij \in \mathcal{E}$有$\phi_{ij}(z) = a_{ij}z$。
不必强调的，对于所有的$ij \in \mathcal{E}$如果有$x_i = x_j$，那么$u=0$。
因此，我们证明收敛性：$u=$表明所有的节点都是一致的。
如果所有节点的值豆娘等，那么结果正确。
因此，假设存在一个节点$i^*$，称作最大领导者，那么对所有的$j\ne i^*$有$x_{i^*}\ge x_j$，即$i^* = arg\max_{j\in \mathcal{I} x_j}$（即如果$i^*$并不是唯一的，可以任意选择）。

{\color[gray]{0.5}
Deﬁne the initial cluster $J^{(0)}=\{ i^* \}$ and denote the indices of all the ﬁrst-neighbors of $i^*$ by $J^{(1)}=N_{i^*}$. 
Then, $u_{i^*}=0$ implies that
}

定义初始化簇$J^{(0)}=\{ i^* \}$并且用$J^{(1)}=N_{i^*}$来表示所有关于$i^*$的第一邻居序列。
那么，$u_{i^*}=0$意味着

\begin{equation}
    \tag{45}
    \label{45}
    \sum_{j\in N_{i^*}} \phi_{i^*j}(x_j-x_{i^*}) = 0
\end{equation}

{\color[gray]{0.5}
\noindent Since $x_j\le x_{i^*}$ for all $j\in N_{i^*}$ and $\phi_{ij}(z)\le 0$ for $z\le 0$ (i.e. all weights are nonnegative), we get $x_{i^*}=x_j$ for all the ﬁrst-neighbors $j\in J^{(1)}$, (i.e. the max-leader and all of its ﬁrst-neighbors are in agreement). 
Next, we deﬁne the $k$th-neighbors of $i^*$ and show that the max-leader is in agreement with all of its $k$th-neighbors for $k = 1,\dots, n − 1$. 
The set of $k$th-neighbors of $i^*$ is defined by the following recursive equation
}

\noindent 由于对所有的$j\in N_{i^*}$有$x_j\le x_{i^*}$，对$z\le 0$有$\phi_{ij}(z)\le 0$（即所有的权重都是非负的），我们对所有的第一邻居$j\in J^{(1)}$有$x_{i^*}=x_j$（即最大领导者和所有它的第一邻居是一致的）。
下一步，我们定义$i^*$的第$k$个邻居并证明当最大领导者一致时所有它的$k$个邻居都是一致的，$k = 1,\dots, n − 1$。
关于$i^*$的第$k$个邻居定义为下述递归公式

\begin{equation}
    \tag{46}
    \label{46}
    J^{(k)} = J^{(k-1)} \cup N_{J^{(k-1)}},\quad k\ge 1, J^{(0)}=\{i^*\}
\end{equation}

{\color[gray]{0.5}
\noindent where $N_J$ denotes the set of neighbors of cluster $J\subseteq\mathcal{I}$ (see equation (1)). 
By definition, $\{i^*\}\subset J^{(k)} \subseteq \mathcal{I}$ for $k\ge1$ and $J^{(k)}$ is a monotonically increasing sequence of clusters (in terms of inclusion). 
}

\noindent 这里$N_J$表示簇$J\subseteq\mathcal{I}$的邻居部分。
根据定义，对于$k\ge1$有$\{i^*\}\subset J^{(k)} \subseteq \mathcal{I}$并且$J^{(k)}$是一个关于推论的单调递增序列。

{\color[gray]{0.5}
Notice that in a strongly connected digraph, the maximum length of the minimum path connecting any node $j\ne i^*$ to node $i^*$ is $n-1$. 
Thus, $J^{(n-1)} = \mathcal{I}$. 
By induction, we prove that all the nodes in $J^{(k)}$ are in agreement for $k\ge 1$. 
The statement holds for $k=1$ (i.e. the set of first-neighbors of the max-leader). 
Assume all the nodes in $J^{(k)}$ are in agreement with $i^*$, we show that all the nodes in $J^{(k+1)}$ are in agreement with $i^*$ as well. 
It is sufficient to show this for an arbitrary node $i\in J^{(k)}$ with $N_i \cap (J^{(k+1)}\setminus J^{(k)}) \ne \emptyset$. 
Otherwise, because in a strongly connected digraph $N_i \ne \emptyset$ for all $i$, we get $J^{(k+1)}=J^{(k)}$ and the statement holds. 
For node $i$, we have
}

注意在一个强连通图中，任意节点$j\ne i^*$和节点$i^*$的最短连接路径的最大长度为$n-1$。
因此，$J^{(n-1)} = \mathcal{I}$。
通过归纳法，我们证明在$J^{(k)}$中所有节点对于$k\ge 1$是一致的。
状态满足$k=1$（即最大领导者的第一邻居部分）。
假设所有$J^{(k)}$中的节点都是关于$i^*$一致的，我们也证明了所有在$J^{(k+1)}$中的节点也是关于$i^*$一致的。
可以充分证明对于任意状态节点$i\in J^{(k)}$有$N_i \cap (J^{(k+1)}\setminus J^{(k)}) \ne \emptyset$。
否则的话，因为强连通图关于所有$i$都有$N_i \ne \emptyset$，我们有$J^{(k+1)}=J^{(k)}$并且状态满足。
对于节点$i$，我们有

\begin{equation}
    \tag{47}
    \label{47}
    u_i = \sum_{j\in N_i} \phi_{ij}(x_j-x_i)=0
\end{equation}

{\color[gray]{0.5}
\noindent But $N_i=(N_i\cap J^{(k)})\cup(N_i\cap(\mathcal{I}\setminus J^{(k)}))$ and $\mathcal{I}\setminus J^{(k)}=\mathcal{I}\setminus J^{(k+1)}\cup (J^{(k+1)}\setminus J^{(k)})$. 
Keeping in mind that $J^{(k)}\subset equ\mathcal{I}$ for all $k$ and $J^{(k+1)}$ contains the set of first neighbors of node $i$, i.e. $N_i\subseteq J^{(k+1)}$, we have
}

\noindent 但是$N_i=(N_i\cap J^{(k)})\cup(N_i\cap(\mathcal{I}\setminus J^{(k)}))$ 且 $\mathcal{I}\setminus J^{(k)}=\mathcal{I}\setminus J^{(k+1)}\cup (J^{(k+1)}\setminus J^{(k)})$。
谨记对所有$k$有$J^{(k)}\subset equ\mathcal{I}$且$J^{(k+1)}$包含了节点$i$的第一邻居部分，即$N_i\subseteq J^{(k+1)}$，我们有

\begin{equation}
    \tag{48}
    \label{48}
    N_i \cap (\mathcal{I}\setminus J^{(k)}) = N_i \cap (J^{(k+1)}\setminus J^{(k)})
\end{equation}

{\color[gray]{0.5}
\noindent and
}

\noindent 和

\begin{equation}
    \tag{49}
    \label{49}
    u_i = \sum_{j\in N_i \cap J^{(k)}} \phi_{ij}(x_j-x_i) + \sum_{j\in N_i \cap (J^{(k+1)}\setminus J^{(k)})} \phi_{ij}(x_j-x_i) = 0
\end{equation}

{\color[gray]{0.5}
\noindent The first sum is equal to zero because $x_j=x_i$ all nodes $j\in N_i \cap J^{(k)} \subseteq J^{(k)}$. 
Thus, the second sum must be zero. 
But $x_{i^*}=x_i\ge x_j$ for all $i\in J^{(k)}$ and $j\in \mathcal{I}\setminus J^{(k)}$ which implies all nodes in $N_i \cap (J^{(k+1)}\setminus J^{(k)})$ are in agreement with $i^*$. 
This means that all nodes in the cluster
}

\noindent 因为所有$j\in N_i \cap J^{(k)} \subseteq J^{(k)}$的节点$x_j=x_i$，所以第一求和为0。
因此，第二求和必须也为0。
但是对于所有的$i\in J^{(k)}$和$j\in \mathcal{I}\setminus J^{(k)}$有$x_{i^*}=x_i\ge x_j$，这表明所有在$N_i \cap (J^{(k+1)}\setminus J^{(k)})$中的节点关于$i^*$一致。
这意味着所有簇中的节点

\begin{equation}
    \tag{50}
    \label{50}
\begin{aligned}
    \cup_{i\in J^{(k)}} N_i \cap (J^{(k+1)} \setminus J^{(k)}) &= (\cup_{i\in J^{(k)}} N_i) \cap (J^{(k+1)} \setminus J^{(k)})\\
    &= J^{(k+1)} \cap (J^{(k+1)} \setminus J^{(k)})\\ 
    &= J^{(k+1)} \setminus J^{(k)}
\end{aligned}
\end{equation}

{\color[gray]{0.5}
\noindent are in agreement with $i^*$, i.e. all the nodes in $J^{(k+1)}$ are in agreement. 
Combining this with the fact that $J^{(n-1)}=\mathcal{I}$ we conclude that all the nodes in $\mathcal{I}$ are in agreement.
}

\noindent 是关于节点$i^*$一致，即所有在$J^{(k+1)}$的节点都一致。
结合$J^{(n-1)}=\mathcal{I}$我们可以推断所有在$\mathcal{I}$中的节点一致。

\subsection*{A.2 Proof of Theorem 10}

{\color[gray]{0.5}
\noindent Notice that despite the existence of a nonzero delay $\tau, \sum_{i=1}^{n} u_i=0$. 
Thus, $\alpha=Ave(x)$ is an invariant quantity. 
Given that the solutions of (37) globally asymptotically converge to a limit $x^*$, due to the invariance of $\alpha$, $x_i^*=Ave(x(0)), \forall i \in \mathcal{I}$ and the average-consensus will be reached. 
To establish the stability of (37), we use a frequency domain analysis. 
We have $X(s) = G_{\tau}(s)x(0)$ where
}

\noindent 注意尽管存在一个非零时滞$\tau, \sum_{i=1}^{n} u_i=0$。
因此，$\alpha=Ave(x)$是一个不变量。
给出以下事实，公式（37）全局渐进收敛到$x^*$，由于$\alpha$的不变性，$x_i^*=Ave(x(0)), \forall i \in \mathcal{I}$，并且一致性是可以达到的。
为了建立（37）的稳定性，我们使用频域分析。
我们有$X(s) = G_{\tau}(s)x(0)$这里

\begin{equation}
    \tag{51}
    \label{51}
    G_{\tau}(s) = (sI_n + e^{-\tau s}L)^{-1}
\end{equation}

{\color[gray]{0.5}
\noindent Define $Z_{\tau}(s) = G_{\tau}^{-1}(s) = (sI_n + e^{-\tau s}L)$. 
We need to find sufficient conditions such that all the zeros of $Z_{\tau}(s)$ are on the open LHP or $s=0$. 
Let $w_k$ be the $k$th normalized eigenvector of $L$ associated with the eigenvalue $\lambda_k$ in an increasing order. 
For a connected graph $G$, $0=\lambda_1 < \lambda_2 \le \dots \le \lambda_n =\lambda_{max}(L)$. 
Clearly, $s=0$ in the direction $w_1$ is a zero of the MIMO transfer function $Z_{\tau}(s)$, because $Z_{\tau}(0)w_1 = Lw_1 = 0$. 
Futhermore, any eigen vector of $Z_{\tau}(s)$ is an eigen vector of $L$ and {\color{green}vice verse}. 
Let ($s,w_k$) with $k>1$ be a right MIMO transmission zero of $Z_{\tau}(s)$ at frequency $s$ in the direction $w_k$, i.e. $Z_{\tau}(s)w_k=0$. 
Then, $s\ne0$ satisfies the following equation
}

\noindent 定义$Z_{\tau}(s) = G_{\tau}^{-1}(s) = (sI_n + e^{-\tau s}L)$。
我们需要找到一个充分条件如所有$Z_{\tau}(s)$的0都是在开放LHP或$s=0$。
定义$w_k$是$L$关于特征值$\lambda_k$递增顺序排列的第$k$个标准化特征向量。
对于一个连通图$G$，有$0=\lambda_1 < \lambda_2 \le \dots \le  \lambda_n =\lambda_{max}(L)$。
清楚的，在方向$w_1$中$s=0$是MIMO转移函数$Z_{\tau}(s)$的0值，因为$Z_{\tau}(0)w_1 = Lw_1 = 0$。
进一步说，任何关于$Z_{\tau}(s)$的特征向量都是一个属于$L$的特征向量和代替。
定义($s,w_k$)$k>1$是一个在频域$s$属于方向$w_k$上关于$Z_{\tau}(s)$右MIMO转移0，即$Z_{\tau}(s)w_k=0$。
那么，$s\ne0$满足下述方程

\begin{equation}
    \tag{52}
    \label{52}
    s+e^{-\tau s}\lambda_k = 0
\end{equation}

{\color[gray]{0.5}
\noindent or
}

\noindent 或

\begin{equation}
    \tag{53}
    \label{53}
    \frac{1}{\lambda_k} + \frac{e^{-\tau s}\lambda_k}{s} = 0
\end{equation}

{\color[gray]{0.5}
\noindent where $\lambda_k$ is the $k$th eigenvalue of $L$ corresponding to $w_k$. 
This is due to the fact that
}

\noindent 这里$\lambda_k$是$L$关于$w_k$的第$k$个特征值。
这是因为

\begin{equation}
    \tag{54}
    \label{54}
    Z_{\tau}(s) w_k = sw_k + e^{-\tau s}Lw_k = (s+e^{-\tau s}\lambda_k)w_k = 0
\end{equation}

{\color[gray]{0.5}
\noindent but $w_k\ne 0$, thus $s+e^{-\tau}\lambda_k=0$. 
Equation (53) provides a Nyquist criterion for convergence of protocol (A2). 
If the net encirclement of the Nyquist plot of $\Gamma(s) = e^{-\tau s}/s$ around $-1/\lambda_k$ for $k>1$ is zero, then all the zeros of $Z_\tau(s)$(or poles of $G_{\tau}(s)$) other than $s=0$ are stable.
For the special case where $L$ is symmetric, all the eigenvalues are real and {\color{green}the Nyquist stability criterion reduces to zero net encirclement of the Nyquist plot of $\Gamma(s)$ around $-1/\lambda_n$ (note that $\lambda_n=\lambda_{max}(L))$.} 
This is because the plot of $\Gamma(jw)$ in the s-plane remains on the right hand side of $-\tau$. 
Since
}

\noindent 但是$w_k\ne 0$，因此$s+e^{-\tau}\lambda_k=0$。
公式（53）协议（A2）收敛分析的奈奎斯特准则。
如果$\Gamma(s) = e^{-\tau s}/s$在$-1/\lambda_k$其中$k>1$附近的网络包围是0，那么所有属于$Z_\tau(s)$的0值（或$G_{\tau}(s)$的极点）不是$s=0$是稳定的。
关于$L$是对称的特殊情况，所有的特征值都是实数并且奈奎斯特稳定准则减小到0。
这是因为$\Gamma(j\omega)$在s平面的图保持在右平面即$-\tau$。
由于

\begin{equation}
    \tag{55}
    \label{55}
    \Gamma(j\omega) = \frac{e^{-j\omega\tau}}{j\omega} = -\frac{sin(\omega\tau)}{\omega} -j\frac{cos(\omega\tau)}{\omega}
\end{equation}

{\color[gray]{0.5}
\noindent and clearly $Re(\Gamma(j\omega))$ is sinc function satisfying $Re(\Gamma(j\omega)) \ge -\tau$. 
A conservative upper bound on $\tau$ can be obtained according to the property $Re(\Gamma(j\omega)) \ge -\tau$ of the Nyquist plot of $\Gamma(s)$ by setting $-1/\lambda_n > -\tau$ which gives the convergence condition $\tau < 1/\lambda_n$. 
As a by-product, for $\tau=0$, the protocol always converges regardless of the value of $\lambda_k, k>1$. 
}

\noindent 并且$Re(\Gamma(j\omega))$是一个满足$Re(\Gamma(j\omega)) \ge -\tau$的sinc函数。
一个在$\tau$上的保守上界。

{\color[gray]{0.5}
A better upper bound on the time-delay $\tau$ can be calculated as follows. 
Let us find the smallest value of the time-delay $\tau>0$ such that $Z_{\tau}(s)$ has a zero on the imaginary axis. 
To do so, set $s=j\omega$ in (52), we have
}

\begin{equation}
    \tag{56}
    \label{56}
    \begin{aligned}
        j\omega + e^{-j\omega\tau} \lambda_k = 0,\\
        -j\omega + e^{j\omega\tau} \lambda_k = 0,
    \end{aligned}
\end{equation}

{\color[gray]{0.5}
\noindent multiplying both sides of the last two equations gives
}

\begin{equation}
    \tag{57}
    \label{57}
    \omega^2 + \lambda_k^2 + j\omega\lambda_k(e^{j\omega\tau}-e^{-j\omega\tau})=0,
\end{equation}

{\color[gray]{0.5}
\noindent or
}

\begin{equation}
    \tag{58}
    \label{58}
    \omega^2 + \lambda_k^2 - 2\omega\lambda_k sin(\omega\tau)=0.
\end{equation}

{\color[gray]{0.5}
\noindent Assuming $\omega>0$ (due to $s\ne 0$), from (58), we get
}

\begin{equation}
    \tag{59}
    \label{59}
    (\omega-\lambda_k)^2 + 2\omega\lambda_k(1-sin(\omega\tau)) = 0.
\end{equation}

{\color[gray]{0.5}
\noindent Since both terms in the left hand side of the last equation are positive semi-deﬁnite, the equality holds if and only if both terms are zero, i.e.
}

\begin{equation}
    \tag{60}
    \label{60}
    \begin{aligned}
        \omega = \lambda_k,\\
        sim(\omega\tau) = 1,
    \end{aligned}
\end{equation}

{\color[gray]{0.5}
\noindent This implies $\tau\lambda_k = 2l\pi + \pi/2$ for $l=0,1,2,\dots$, thus the smallest $\tau>0$ satisfies $\tau\lambda_k=\pi/2$. 
Therefore, we have
}

\begin{equation}
    \tag{61}
    \label{61}
    \tau^* = \min_{\substack{\tau\lambda_k=\pi/2\\k>1}}\{\tau\} = \min_{k>1}\frac{\pi}{2\lambda_k}=\frac{\pi}{2\lambda_n}
\end{equation}

{\color[gray]{0.5}
\noindent Due to the continuous dependence of the roots of equation (52) in $\tau$ and the fact that all the zeros of this equation other than $s=0$ for $\tau=0$ are located on the open LHP, for all $\tau\in(0, \tau^*)$, the roots of (52) with $k>1$ are on the open LHP and therefore the poles of $G_{\tau}(s)$ (except for $s=0$) are all stable. 
One can repeat a similar argument for the assumption that $\omega<0$ and get the equation
}

\begin{equation}
    \tag{62}
    \label{62}
    (\omega+\lambda_k)^2 - 2\omega\lambda_k(1+sin(\omega\tau))=0,
\end{equation}

{\color[gray]{0.5}
\noindent which leads to $\omega=-\lambda_k$ and $\tau\lambda_k = 2l\pi + \pi/2$. 
}

{\color[gray]{0.5}
For $\tau=\tau^*$, $G_{\tau}(s)$ has three poles on the imaginary axis given by 
}

\begin{equation}
    \tag{63}
    \label{63}
    s = 0, s \pm j\lambda_n
\end{equation}

{\color[gray]{0.5}
\noindent All other poles of $G_{\tau}(s)$ are stable and in the steady-state the values of each node takes the following form: 
}

\begin{equation}
    \tag{64}
    \label{64}
    x_i^{ss}(t) = a_i + b_i sin(\lambda_nt + \varphi_i),\quad i\in\mathcal{I}
\end{equation}

{\color[gray]{0.5}
\noindent where $a_i,b_i,\varphi_i$ are constants that depend on the initial conditions. 
}

\section*{References}
\noindent [1] N. Biggs. Algebraic Graph Theory. Cambridge Tracks in Mathematics. Cambridge University Press, 1974.

\noindent [2] I. Daubechies and J. C. Lagarias. Sets of matrices all inﬁnite products of which converge. Linear Algebra and Its Applications, 161:227–263, 1992.

\noindent [3] I. Daubechies and J. C. Lagarias. Corrigendum/addendum to: Sets of matrices all inﬁnite products of which converge. Linear Algebra and Its Applications, 327:69–83, 2001.

\noindent [4] J. P. Desai, J. P. Ostrowski, and V. Kumar. Modeling and control of formations of nonholonomic mobile robots. IEEE Trans. on Robotics and Automation, 17(6), December 2002.

\noindent [5] R. Diestel. Graph Theory, volume 173 of Graduate Texts in Mathematics. SpringerVerlag, 2000.

\noindent [6] A. Fax and R. M. Murray. Graph Laplacians and stabilization of vehicle formations. The 15th IFAC World Congress, June 2002.

\noindent [7] A. Fax and R. M. Murray. Information Flow and Cooperative Control of Vehicle Formations. The 15th IFAC World Congress, June 2002.

\noindent [8] M. Fiedler. Algebraic connectivity of graphs. Czechoslovak Mathematical Journal, 23(98):298–305, 1973.

\noindent [9] M. Fiedler. A property of eigenvectors of nonnegative symmetric matrices and its application to graph theory. Czechoslovak Mathematical Journal, 25(100):619–633, 1975.

\noindent [10] F. R. Gantmacher. Matrix Theory, volume II. Chelsea Publishing Company, 1959.

\noindent [11] C. Godsil and G. Royle. Algebraic Graph Theory, volume 207 of Graduate Texts in Mathematics. Springer, 2001.

\noindent [12] R. A. Horn and C. R. Johnson. Matrix Analysis. Cambridge University Press, 1987.

\noindent [13] A. Jadbabaie, J. Lin, and S. A. Morse. Coordination of groups of mobile agents using nearest neighbor rules. IEEE Trans. on Automatic Control (to appear).

\noindent [14] R. W. Lawton, J. R. T. Beard and B. J. Young. A Decentralized Approach to Formation Maneuvers. IEEE Trans. on Robotics and Automation (to appear).

\noindent [15] N. A. Lynch. Distributed Algorithms. Morgan Kaufmann Publishers, Inc., 1997.

\noindent [16] M. Marcus and H. Minc. A Survey of Matrix Theory and Matrix Inequalities. Dover Publications, 1969.

\noindent [17] R. Merris. Laplacian matrices of a graph: a survey. Linear Algebra and its Applications, 197:143–176, 1994.

\noindent [18] M. Mesbahi. On a dynamic extension of the theory of graphs. Proc. of the American Control Conference, Anchorange, AL, May 2002.

\noindent [19] M. Mesbahi and F. Y. Hadegh. Formation ﬂying of multiple spacecraft via graphs, matrix inequalities, and switching. AIAA Journal of Guidance, Control, and Dynamics, 24(2):369–377, March 2000.

\noindent [20] R. Olfati Saber and R. M. Murray. Consensus Protocols for Networks of Dynamic Agents. Proc. of the American Control Conference, June 2003.

\noindent [21] F. Paganini, J. Doyle, and S Low. Scalable laws for stable network congestion control. Proc. of the Int. Conf. on Decision and Control, Orlando, FL, Dec. 2001.

\noindent [22] C. W. Reynolds. Flocks, herds, and schools: a distributed behavioral model. Computer Graphics (ACM SIGGRAPH ’87 Conference Proceedings), 21(4):25–34, July 1987.

\noindent [23] J. Toner and Y. Tu. Flocks, herds, and schools: A quantitative theory of ﬂocking. Physical Review E, 58(4):4828–4858, October 1998.

\noindent [24] T. Vicsek, A. Cziro´ok, E. Ben-Jacob, and O. Cohen, I. Shochet. Novel type of phase transition in a system of self-deriven particles. Physical Review Letters, 75(6):1226–1229, August, 1995.

\noindent [25] H. Yamaguchi, T. Arai, and G. Beni. A distributed control scheme for multiple robotic vehicles to make group formations. Robotics and Autonomous Systems, 36:125–147, 2001
